%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventrywithsummary
{Lead DevOps Engineer} % Job title
{Sanctuary AI} % Organization
{Vancouver} % Location
{Nov 2022 - Dec 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Managed the DevOps \& MLOps team.}
    \item {Hired \& bar-raised for DevOps, Software Engineering \& Manager roles.}
    \item {Built \& operated CI/CD pipelines for multiple services \& applications.}
    \item {Designed \& developed services to improve scalability and efficiency of Sanctuary AI's cognitive architecture.}
    \item {Architected decentralized data capture \& offload system for the Phoenix robots}
    \item {Mentored Junior Engineers \& Co-Ops to advance their SRE \& Software Engineering skills}
  \end{cvitems}
}
{
  Sanctuary AI is on a mission to create the world's first human-like intelligence in general-purpose robots.
  Its humanoid robot Phoenix won a TIME magazine award for best invention of 2023 in the robotics category.
}

%---------------------------------------------------------
\cventrywithsummary
{Senior Infrastructure Engineer} % Job title
{CubicFarm Systems} % Organization
{Remote} % Location
{May 2022 - Sep 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Constructed and operated a microservice architecture software stack for the Hydrogreen product line.}
    \item {Deployed control systems software for IoT edge devices, a web API and a front-end web application to support Hydrogreen.}
    \item {Developed and maintained build pipelines for the over 20 microservices comprising the architecture for CubicFarms and Hydrogreen.}
  \end{cvitems}
}
{
  CubicFarm Systems is a controlled-environment agriculture company that specializes in automated hydroponic farming.
  They have two product lines: CubicFarms for leafy greens and Hydrogreen for livestock feed.
}

%---------------------------------------------------------
\cventrywithsummary
{Self Employed - Software Engineering \& DevOps Consultant} % Job title
{Dieter Buys Consulting} % Organization
{Remote \& On-Site} % Location
{Feb 2018 - Nov 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {For HSBC International I joined their mobile banking team to evolve their build infrastructure \& release management for the HSBC mobile banking application that served tens of millions of users and transacted billions of dollars annually. The application had over 1,000 builds a day on a hybrid cloud \& on-prem Jenkins cluster with more than 200 nodes to produce 43 localized variants of the application on iOS and Android platforms. This achieved a dramatic increase in developer velocity and release cadence. In addition, I built custom tooling for observability and release management to surface critical information to the application developers and release managers about feature flags, build status and release readiness. I also hired and mentored the Canadian members of the team to continue this work.}
    \item {For Tally Inc., a Silicon Valley startup that provides an innovative debt management application, I migrated their primary website from an unmaintained Wordpress installation to a managed cloud-based solution using Contentful and transferred the content management to a subcontractor for long-term maintenance. This involved migrating from an EC2 hard-coded instance to a highly available, observable and cost-efficient ECS cluster and developing a CI/CD pipeline that would enable safe \& frequent updates to the base content management system and plugins to ensure security and reliability going forward. I also mentored engineers on the team to cultivate their cloud infrastructure skillset such as migrating from 5 distinct VPNs to 1 unified VPN with role-based access control.}
  \end{cvitems}
}
{
  Proprietor of my own consulting company providing Software Engineering \& DevOps services to clients in Banking, Finance and Ag Tech. I would interface with clients to determine their unique needs \& identify opportunities for improvement in efficiency, cost savings and reliability in their software stacks. Following this we would negotiate a contract with a typical duration about 1 year, although one client (HSBC Bank) renewed twice for a total of 3 years. The results would be permanent improvements to their infrastructure, development methodology, tools or teams built to meet their ongoing needs. Some examples of this work:
}

%---------------------------------------------------------
% \cventrywithsummary
% {Consulting Software Engineer} % Job title
% {Tally Inc.} % Organization
% {Remote} % Location
% {Feb 2021 - Oct 2021} % Date(s)
% {
% \begin{cvitems} % Description(s) of tasks/responsibilities
% \item {Handled migration of primary website (www.meettally.com) from in-house Wordpress to Contentful managed by a subcontractor.}
% \item {Drove the upgrading of the website from hand-crafted EC2 instances to ECS cluster defined in Terraform, with much improved availability, security, observability and maintainability.}
% \item {Mentored intermediate engineer and assisted in her task of consolidating the company's 5 VPNs down to 1.}
% \end{cvitems}
% }
% {
% Tally Inc. is a financial automation company that provides consolidation and repayment assistance for credit card debt.
% }

% %---------------------------------------------------------
% \cventrywithsummary
% {Consulting Software Engineer} % Job title
% {HSBC Digital} % Organization
% {Vancouver \& Remote} % Location
% {Feb 2018 - Feb 2021} % Date(s)
% {
% \begin{cvitems} % Description(s) of tasks/responsibilities
% \item {Responsible for operating, evolving and scaling the CICD pipeline for the HSBC cross-platform mobile app supporting over 60 developers 24/7/365 across 4 time zones, producing over 1,000 builds a day for 43 locales using a hybrid Jenkins cluster with more than 100 nodes.}
% \item {Developer and maintainer of custom tooling for developers, managers and bankers to streamline development and enhance product quality.}
% \item {Hired and trained engineers to meet the unique security and regulatory challenges of the banking sector as well as the enormous organizational scale at HSBC. }
% \end{cvitems}
% }
% {
% HSBC Digital is the division of HSBC International that develops and operates the HSBC mobile application (which has over 1.34 million active users), websites \& web applications, and R&D for various digital innovation products.
% }

%---------------------------------------------------------
\cventrywithsummary
{Senior Software Engineer} % Job title
{Urthecast Inc. (now EarthDaily Analytics)} % Organization
{Vancouver} % Location
{Oct 2015 - Feb 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Key contributor to the planning, architecting and development of the next generation optical processing pipeline, data repository, calibration and validation system and testing framework.}
    \item {Co-authored a successful proposal worth \$1.1 million for the Canada's Innovation Supercluster initiative, a public-private-academic partnership involving Urthecast, the University of Victoria and Microsoft Canada to define a new standard for integrating diverse geospatial data into a single platform to democratize access and facilitate innovative research.}
    \item {Contributed significant code to enhance the architecture of the optical processing pipeline. Also implemented a reprojection \& tiling subsystem for sensor cross-calibration.}
    \item {One of two engineers assigned to take over the legacy data platform from the Urthecast office in San Francisco. I became a maintainer of the back-end services, the web application and the data packaging service, to which I made significant improvements including a 4x reduction in storage cost and 2x increase in resampling performance.}
    \item {Co-developed an automated process to migrate more than a petabyte of indexed geospatial data from raw data on S3 to a compressed format with an archiving system based on Glacier and S3.}
  \end{cvitems}
}
{
  Urthecast owned and operated 4 advanced orbital optical sensors (2 satellites and 2 on the ISS) to provide scientific-grade satellite imagery for Agriculture, Science, Urban Planning, Insurance, Intelligence and other applications. As one of Canada's largest aerospace companies, they were also leaders in developing a scalable optical data processing pipeline and a platform for delivering geospatial data from a vast catalogue spanning a diverse set of sources.
}

%---------------------------------------------------------
\cventrywithsummary
{Software Engineer} % Job title
{Prior Work} % Organization
{Vancouver} % Location
{2006 - 2015} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {I was responsible for feature additions and operational maintenance of back-end services for matchmaking, leaderboards and stats tracking to serve millions of users, with request rates in the tens of thousands per second. These services were hybrid with some being hosted on-premise and others using cloud providers. They had to be secure against frequent denial of service attacks and hacking attempts. These services supported live-service gameplay and integrations with mobile \& web applications.}
    \item {I led a team to create a custom isometric engine for a web-based hidden-object game with innovative rendering technology and custom tools that allowed for procedural content generation \& seamless integrations with social media platforms such as Facebook. The game featured a simulation system for a population of procedurally-generated characters, a quest system, a dialogue system for story exposition as well as detailed metrics tracking for in-game events.}
    \item {I developed gameplay (weapons, AI, physics, scripted events) \& rendering code (shaders, heads-up displays, menu systems) for numerous titles across platforms such as Playstation 3, XBox 360, PC native applications as well as for the web.}
  \end{cvitems}
}
{
  Prior to 2015 I was a Software Engineer in the video games industry at \textit{Electronic Arts}, \textit{Activision Blizzard} and other companies,
  with credits including \textit{Call of Duty: Advanced Warfare}, \textit{Diablo III - Reaper of Souls} and \textit{Army of Two}. Some highlights from this period:
}

%---------------------------------------------------------
\end{cventries}